---
title: "HIPAA Identifiers Report"
subtitle: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 10pt
geometry: margin=0.5cm
output:
  pdf_document:
    includes:
        in_header: mySty.sty
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(xtable.comment = FALSE,echo = FALSE,comment=NA,message=FALSE, warning=FALSE)
```

\pagebreak

###Copy of DeepSee_Diaceutics_20170208_20170228_v1.csv

```{r f1,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Copy of DeepSee_Diaceutics_20170208_20170228_v1.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}


if(nrow(report$getNameChanges()>0)){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}


 
```


\clearpage


###DeepSee_Diaceutics_20170301_20170320v2_deiddb.csv


```{r f25,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("DeepSee_Diaceutics_20170301_20170320v2_deiddb.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatientIdentifiers()>0)){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}


if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```

\clearpage


###diaceutic query 2_deid.csv

```{r f2,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("diaceutic query 2_deid.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatientIdentifiers()>0)){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}


if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

  
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage


###Diaceutics 032117_033117v3.csv

```{r f3,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Diaceutics 032117_033117v3.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage

###Diaceutics 04012017_04132017deid.csv


```{r f4,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Diaceutics 04012017_04132017deid.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage


###Diaceutics onco 020817_032017_deid_db.csv

```{r f5,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Diaceutics onco 020817_032017_deid_db.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage


###Diaceutics v2_deid_061517.csv

```{r f6,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Diaceutics v2_deid_061517.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=100L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```

\clearpage

###diaceutics_0701_312017_deid.csv

```{r f7,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("diaceutics_0701_312017_deid.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=60L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" ,tabular.environment="longtable")
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```

\clearpage


###Diaceutics_20170114_20170207_new1_update.csv

```{r f8,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Diaceutics_20170114_20170207_new1_update.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=60L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" ,tabular.environment="longtable")
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage

###LBCL_010116_043017_deid.csv

```{r f9,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("LBCL_010116_043017_deid.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=60L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" ,tabular.environment="longtable")
}
# 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```
\clearpage

###Oncolgy_Diaceuticsv3_1211_0113.csv

```{r f10,results="asis"}

source("Report.r")
     
library(knitr)
library(data.table)
library(xtable)
options(xtable.comment = FALSE)

     reportParams = ReportParameters$new(dataFile=tolower("Oncolgy_Diaceuticsv3_1211_0113.csv"), showOriginal = FALSE,extractedTextLength=95L, instancesToShow=60L,   wrapTextWidth=40L )
report<-Report$new(reportParams)

safeDataFileName<-gsub('_', ' ', reportParams$dataFile)

print(xtable(report$ShowTotalsdt(),align= c("|p{0cm}|", "p{6cm}|" ,"p{11cm}|"),caption=paste0(safeDataFileName," totals")),include.rownames=FALSE,caption.placement = "top")


if(nrow(report$getSurgicalNumbers())>0){
 tab<- xtable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " surgical numbers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" ,tabular.environment="longtable")
}
 
if(nrow(report$getPatientIdentifiers())>0){
 tab<- xtable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " patient identifiers"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getNameChanges())>0){
 tab<- xtable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption=paste0(safeDataFileName, " name changes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getpatientDateOfBirth())>0)
{
 tab<- xtable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=60)),caption=paste0(safeDataFileName, " patient date of birth"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  names(tab) <- c('Row','Text' )
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatDates())>0)
{
 tab<- xtable(as.data.table(head(report$getPatDates()[,c("rownumber","patient draw date")],n=60)),caption=paste0(safeDataFileName, " patient draw dates"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getPatAgeOverMax())>0)
{
 tab<- xtable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patient age over max")],n=60)),caption=paste0(safeDataFileName, " patient age over max"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}
if(nrow(report$getValidZipCodes())>0)
{
 tab<- xtable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","patient address postal code")],n=60)),caption=paste0(safeDataFileName, " valid zip codes"),align= c("p{0cm}|", "p{2cm}|" ,"p{15cm}|"))
  print(tab,include.rownames=FALSE,caption.placement = "top" )
}

 
```


