---
title: "Diaceutics PI Report 02/09/2016"
fontsize: 10pt
geometry: margin=0.5cm
output:
  pdf_document:
    includes:
        in_header: mySty.sty
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,comment=NA,message=FALSE, warning=FALSE,fig.align="center")
```



###Copy of DeepSee_Diaceutics_20170208_20170228_v1.csv
```{r pressure}
source("Report.r")

     reportParams = ReportParameters$new(dataFile="Copy of DeepSee_Diaceutics_20170208_20170228_v1.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 



kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  


kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges()>0))
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")


if(nrow(report$getPatAgeOverMax())>0)
kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")

if(nrow(report$getValidZipCodes())>0)
kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")


```


\pagebreak


###DeepSee_Diaceutics_20170301_20170320v2_deiddb.csv
```{r pressure2}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="DeepSee_Diaceutics_20170301_20170320v2_deiddb.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 

if(nrow(report$getSurgicalNumbers()>0))
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers()>0))
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges()>0))
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")


if(nrow(report$getPatAgeOverMax())>0)
kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Examples Of Patient Age Over Max"),align="l")

if(nrow(report$getValidZipCodes())>0)
kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```




\pagebreak


### diaceutic query 2_deid.csv
```{r pressure3}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="diaceutic query 2_deid.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 



if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")


if(nrow(report$getPatAgeOverMax())>0)
kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")

if(nrow(report$getValidZipCodes())>0)
kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```



\pagebreak


###Diaceutics 032117_033117v3
```{r pressure4}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Diaceutics 032117_033117v3.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```
\pagebreak

###Diaceutics 04012017_04132017deid.csv
```{r pressure5}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Diaceutics 04012017_04132017deid.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```
\pagebreak


###Diaceutics onco 020817_032017_deid_db.csv
```{r pressure6}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Diaceutics onco 020817_032017_deid_db.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```

\pagebreak

###Diaceutics v2_deid_061517.csv
```{r pressure7}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Diaceutics v2_deid_061517.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```
\pagebreak


###diaceutics_0701_312017_deid.csv
```{r pressure8}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="diaceutics_0701_312017_deid.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```
\pagebreak

###Diaceutics_20170114_20170207_new1_update.csv
```{r pressure9}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Diaceutics_20170114_20170207_new1_update.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, "  Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```

\pagebreak

###LBCL_010116_043017_deid.csv###
```{r pressure10}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="LBCL_010116_043017_deid.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```

\pagebreak


###Oncolgy_Diaceuticsv3_1211_0113.csv
```{r pressure11}

source("Report.r")

     reportParams = ReportParameters$new(dataFile="Oncolgy_Diaceuticsv3_1211_0113.csv", showOriginal = FALSE,extractedTextLength=90L, instancesToShow=100L, printInstances =FALSE,  wrapTextWidth=40L )


report<-Report$new(reportParams)

     
library(knitr)
library(data.table)
library(kableExtra)

 kable(report$ShowTotalsdt(),caption =  paste0(reportParams$dataFile, " Total Counts"),align="l") 


if(nrow(report$getSurgicalNumbers())>0)
kable(as.data.table(head(report$getSurgicalNumbers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Surgical Numbers"),align="l")  

if(nrow(report$getPatientIdentifiers())>0)
kable(as.data.table(head(report$getPatientIdentifiers()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Identifiers"),align="l") 

if(nrow(report$getNameChanges())>0)
kable(as.data.table(head(report$getNameChanges()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Name Changes"),align="l") 

if(nrow(report$getpatientDateOfBirth())>0)
kable(as.data.table(head(report$getpatientDateOfBirth()[,c("rownumber","obfuscatedtext")],n=reportParams$instancesToShow)), caption = paste0(reportParams$dataFile, " Patient Date Of Birth"),align="l") 

if(nrow(report$getPatDates())>0)
kable(as.data.table(head(report$getPatDates()[,c("rownumber","patientdrawdate")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile, " Patient Draw Dates"),align="l")
 
 
 if(nrow(report$getPatAgeOverMax())>0)
 kable(as.data.table(head(report$getPatAgeOverMax()[,c("rownumber","patientage")],n=reportParams$instancesToShow)),caption = paste0(reportParams$dataFile," Patient Age Over Max"),align="l")
 
 if(nrow(report$getValidZipCodes())>0)
 kable(as.data.table(head(report$getValidZipCodes()[,c("rownumber","cleanzipcodes")],n=reportParams$instancesToShow)),caption =  paste0(reportParams$dataFile," Valid Zip Codes"),align="l")





```




